Software Ticket Quality

### 2017-11-15 proposal/mprop.tex
Add where should we fix this bug paper

>>>>

\textbf{Where should we fix this bug?}\cite{kim2013should}:
\begin{itemize}
  \item \textbf{What were the goals?}
    The main goal of the paper was to aid developers in easily finding where to
    apply the necessary changes in order to fix a bug. The authors wanted to bridge
    this gap by creating a two-phase recommendation model that would locate the locations
    where the fixes need to be applied based on the corresponding bug reports.
  \item \textbf{What was the method?}
    They divided the work into multiple stages:
      \begin{itemize}
        \item firstly, they did a feature extraction on the bug reports (e.g. extract
        description, metadata, summary);
        \item in order to predict the locations of the necessary fixes, the one-phase
        recommendation model was put into place - this model would be trained on collected
        bug reports and then, when given a new bug report, it would try to localize the 
        files that need to be changed automatically;
        \item last step was to implement the two-phase recommendation model which basically
        has two classification phases - binary and multiclass:
          \begin{itemize}
            \item binary phase filters out uninformative bug reports before predicting the
            files to fix;
            \item multiclass phase where the previously filtered bug reports are used as
            training data and only after that new bug reports can be analyzed and files to be
            changed recommended.
          \end{itemize}
      \end{itemize}
  \item \textbf{What did they learn?}
    Evaluating the model yielded a 70\% accuracy in pointing to the correct files
    to be fixed, as long as the algorithm actually recommended any locations. However, the authors
    acknowledge that the approach needs extra work, especially in fine-grained defect 
    localization, performance improvement and bug triaging.
  \item \textbf{Relevance to our work}:
    The research shows interesting points regarding time-to-fix-bug and bug report
    contents, thus it can give us an insight into how ticket quality can affect that 
    time to fix the bug (in the case of this paper it would mean to successfully pass the first
    phase of the recommendation model so that fix locations could be proposed).
\end{itemize}
